---
title: "Prediction Assignment Writeup"
author: "Billy Chen"
date: "Aug 23, 2015"
output: html
---

The goal of this project is to predict the manner in which those did the exercise.
The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har.

## Preprocessing Data
1. Delete columns with empty values
2. Delete the first 7 columns which not related to the prediction: X, user_name, raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp, new_window, num_window.

```{r}
library(caret)
set.seed(12463)

training <- read.csv("pml-training.csv", stringsAsFactors=FALSE)
training$classe <- as.factor(training$classe)
training <- training[,-nearZeroVar(training)]
training <- training[,-c(1,2,3,4,5,6,7)]

```


ThereGet rid of NA values using KnnImpute method to impute those values.

```{r}
inTrain <- createDataPartition(y=training$classe, p=0.75, list=FALSE)
training <- training[inTrain,]
testing <- training[-inTrain,]

preObj <- preProcess(training[,-length(training)],method=c("center", "scale", "knnImpute", "pca"), thresh=0.9)
clean_data <- predict(preObj,training[,-length(training)])
```

## Prediction

Knn method will be used to build the model.  The accuracy is 0.9748. 

```{r}
modelFit <- train(training$classe ~.,data=clean_data, method="knn")
test <- predict(preObj, testing[,-length(testing)])
confusionMatrix(testing$classe, predict(modelFit,test))
```


Finally, predict the result with the testing data:

```{r}
testing <- read.csv("pml-testing.csv", stringsAsFactors=FALSE)
testing <- testing[,names(testing) %in% names(training)]

test <- predict(preObj, testing)
result <- predict(modelFit, test)
result
```